Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2024-10-28 paper/paper.tex
fix build

To gain intuiton for working in \theoryabbv, we study some examples of
grammars and parses of them internal to \theoryabbc. In each of our examples, we will look at
grammars over the three character alphabet $\{ a , b , c\}$.

@@

\begin{figure}
\begin{align*}
\data &~\Trace_{N}~1~(acc : \Bool) : L_{i}~\where\\
      & \mathsf{stop}_{1} : \ltonl {\Trace_{N}~1~\true}  \\
      & \mathsf{1to2} : \forall (acc : \Bool) \to \ltonl {(b \lto \Trace_{N}~2~acc \lto \Trace_{N}~1~acc)} \\
      & \mathsf{1to3} : \forall (acc : \Bool) \to \ltonl {(\Trace_{N}~3~acc \lto \Trace_{N}~1~acc)} \\
\\
\data &~\Trace_{N}~2~(acc : \Bool) : L_{i}~\where\\
      & \mathsf{stop}_{2} : \ltonol {\Trace_{N}~2~\false} \\
      & \mathsf{2to2} : \forall (acc : \Bool) \to \ltonl {(a \lto \Trace_{N}~2~acc \lto \Trace_{N}~2~acc)} \\
      & \mathsf{2to3} : \forall (acc : \Bool) \to \ltonl {(b \lto \Trace_{N}~3~acc \lto \Trace_{N}~2~acc)}  \\
\\
\data &~\Trace_{N}~3~(acc : \Bool) : L_{i}~\where\\
      & \mathsf{stop}_{3} : \ltonl {\Trace_{N}~3~\true} \\
      & \mathsf{3to1} : \forall (acc : \Bool) \to \ltonl {(a \lto \Trace_{N}~1~acc \lto \Trace_{N}~3~acc)} \\
\end{align*}
\caption{$N$ as an indexed inductive type}
\label{fig:nfainductive}
\end{figure}

>>>>

To gain intuiton for working in \theoryabbv, we study some examples of
grammars and parses of them internal to \theoryabbv. In each of our examples, we will look at
grammars over the three character alphabet $\{ a , b , c\}$.

@@

\begin{figure}
\begin{align*}
\data &~\Trace_{N}~1~(acc : \Bool) : L_{i}~\where\\
      & \mathsf{stop}_{1} : \ltonl {\Trace_{N}~1~\true}  \\
      & \mathsf{1to2} : \forall (acc : \Bool) \to \ltonl {(b \lto \Trace_{N}~2~acc \lto \Trace_{N}~1~acc)} \\
      & \mathsf{1to3} : \forall (acc : \Bool) \to \ltonl {(\Trace_{N}~3~acc \lto \Trace_{N}~1~acc)} \\
\\
\data &~\Trace_{N}~2~(acc : \Bool) : L_{i}~\where\\
      & \mathsf{stop}_{2} : \ltonl {\Trace_{N}~2~\false} \\
      & \mathsf{2to2} : \forall (acc : \Bool) \to \ltonl {(a \lto \Trace_{N}~2~acc \lto \Trace_{N}~2~acc)} \\
      & \mathsf{2to3} : \forall (acc : \Bool) \to \ltonl {(b \lto \Trace_{N}~3~acc \lto \Trace_{N}~2~acc)}  \\
\\
\data &~\Trace_{N}~3~(acc : \Bool) : L_{i}~\where\\
      & \mathsf{stop}_{3} : \ltonl {\Trace_{N}~3~\true} \\
      & \mathsf{3to1} : \forall (acc : \Bool) \to \ltonl {(a \lto \Trace_{N}~1~acc \lto \Trace_{N}~3~acc)} \\
\end{align*}
\caption{$N$ as an indexed inductive type}
\label{fig:nfainductive}
\end{figure}
